Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-01-19 docs/manuscript/manuscript.tex
added sketch of results comparison table

>>>>

\begin{table}[h!]
  \centering
  \begin{tabular}{l l l l l l l }\toprule
    \bf Model & \multicolumn{3}{c}{\bf Training metrics} &\multicolumn{3}{c}{\bf Validation metrics}  \\\midrule
    & Error & Precision & Recall     & Error & Precision & Recall \\
    SafeTree & & & & & & \\
    GoogleNet (InceptionV3) & & & & & & \\
    ResNet50 & & & & & & \\
        VGGNet & & & & & & \\
    AlexNet & & & & & & \\\bottomrule
  \end{tabular}
  \caption{Comparing our model SafeTree with state-of-the-art CNN architectures trained on our data}
  \label{tab:comp}
\end{table}
